Rotation and Lithium Confirmation of a 500 Parsec Halo for the Open Cluster NGC\,2516\footnote{This is paper 3 of the Cluster Difference Imaging Photometric Survey.}

### 2021-04-26 cluster_paper/maintable_header.tex
update ms

\texttt{Li\_EW\_mA\_perr\_GaiaESO} &              12.407 &                                     Gaia-ESO Li doublet EW upper uncertainty interval [m\AA]. \\
\texttt{Li\_EW\_mA\_merr\_GaiaESO} &                 5.0 &                                     Gaia-ESO Li doublet EW lower uncertainty interval [m\AA]. \\

@@

  \texttt{Li\_EW\_mA\_perr\_GALAH} &                 NaN &                                        GALAH Li doublet EW upper uncertainty interval [m\AA]. \\
  \texttt{Li\_EW\_mA\_merr\_GALAH} &                 NaN &                                        GALAH Li doublet EW lower uncertainty interval [m\AA]. \\

>>>>

\texttt{Li\_EW\_mA\_perr\_GaiaESO} &              12.407 &                                              Gaia-ESO Li doublet EW upper uncertainty [m\AA]. \\
\texttt{Li\_EW\_mA\_merr\_GaiaESO} &                 5.0 &                                              Gaia-ESO Li doublet EW lower uncertainty [m\AA]. \\

@@

  \texttt{Li\_EW\_mA\_perr\_GALAH} &                 NaN &                                                 GALAH Li doublet EW upper uncertainty [m\AA]. \\
  \texttt{Li\_EW\_mA\_merr\_GALAH} &                 NaN &                                                 GALAH Li doublet EW lower uncertainty [m\AA]. \\
